Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-07-28 rebuttal.tex

\begin{document}
\title{Response to reviews of ``Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure''}
\maketitle

We thank the editor and reviewers for their helpful comments, and have addressed their requests and questions here.

\section{Reviewer 1}

\begin{enumerate}
\item \emph{This paper has a really excellent collection of examples and this survey is very valuable. There are two problems. The first is easy to fix and it constitutes the ``minor revision'' requested: expand each acronym at first use. For example, page 3 has NGS, CMB, MODIS, etc. say "Next Generation Sequencing (NGS)", etc.}

@@

\textbf{Response:} \katznote{attention needed here}

\item \emph{``In this paper, we use locally distributed to indicate that data/compute resides on multiple nodes within one data center. Geographically distributed describes the distribution of data and/or compute across multiple data centersâ'' Given the above, I think it would be better in this definition to also separate out data creation location from compute location. Intro: Define precisely what is meant by ``dynamic,'' here as it is key to the paper but isn't well defined in Section 1 (see recommendation above to fix this by moving definitions from Section 3).}

\textbf{Response:} \katznote{attention needed here}

\katznote{partial response:} In addition, recognizing that the two reviewers have different styles of reading
and different areas of expertise (as do we as authors), we have added a paragraph at the end
of Section 1 to explain how different types of readers might want to approach this paper.  We do
not believe that there is one single way of organizing it that would satisfy all readers.

@@

\textbf{Response:} \katznote{attention needed here}

\hspace{-0.7cm}Section 3.

\item \emph{see earlier comments on definitions.}

\textbf{Response:} See earlier response about definitions, in point 4.

### 2016-08-15 3dpas_intro.tex
adding Omer's changes, which some very small changes as well

The remainder of this paper consists of
the application scenarios (\S\ref{sec:scenarios}),
a discussion of the aspects of distribution and dynamism in the
applications (\S\ref{sec:distdyndata}),
a description of the software infrastructure required for D3 applications
% Yogesh: This section's description seemed more verbose than others, hence commenting out details
% , such as
% software frameworks, tools, and middleware and platform services
(\S\ref{sec:infrastructure}),
analysis and characterization of the applications and
conclusions (\S\ref{sec:conclusions}).

>>>>

The remainder of this paper consists of
the application scenarios (\S\ref{sec:scenarios}),
a discussion of the aspects of distribution and dynamism in the
applications (\S\ref{sec:distdyndata}),
a description of the software infrastructure required for D3 applications
% Yogesh: This section's description seemed more verbose than others, hence commenting out details
% , such as
% software frameworks, tools, and middleware and platform services
(\S\ref{sec:infrastructure}),
analysis and characterization of the applications and
conclusions (\S\ref{sec:conclusions}). Each of these sections is briefly described below:

\item Section~\ref{sec:scenarios} provides a description of thirteen D3 applications based on our survey. For each application, both the {\it dynamic} and {\it distributed} aspects are described. The methodology used to carry out the survey is described in the Appendix.

\item Based on the application survey, we derive a set of  definitions for {\it Distribution} and {\it Dynamism} in \S\ref{sec:distdyndata}. Note that these definitions are based on the application survey. A variety of definitions of these concepts already exist in computer science literature. Our intention is
to provide context for the use of these terms with reference to our survey. The distributed and dynamic characteristics of each application surveyed in \S\ref{sec:scenarios} is summarized in this section.

\item In \S\ref{sec:infrastructure}, we subsequently describe the software/systems infrastructure used to support the distributed and dynamic characteristics of applications in \S\ref{sec:scenarios}. We outline support for data management, analysis, and coordination, providing examples of actual Cyberinfrastructure made use of by our surveyed applications for these purposes.

\item In \S\ref{sec:conclusions}, we bring together key observations based on the analysis of applications, their distributed and dynamic characteristics, and infrastructure use. An attempt is made to compare these applications and suggest the need for an ``architecture for D3 science".
